Titeln på avhandlingens språk

### 2023-02-13 body/part1/futurework.tex
futwork

The optimization framework employed in \cref{paper:olguinmunoz2023realistic} to study the implications of our methodology for the optimization of \gls{WCA} could be improved by expanding it towards distributions which better describe the behavior of human execution times.
Currently, the framework assumes executions times are Rayleigh-distributed, however in literature these values are generally understood to follow an \glx{exGaussian} distribution.
Moreover, the utility of the framework could be significantly increased by considering extensions towards scenarios with multiple clients and a distributed solution.

>>>>

The optimization framework employed in \cref{paper:olguinmunoz2023realistic} to study the implications of our methodology for the optimization of \gls{WCA} could be improved by expanding it towards distributions which better describe the behavior of human execution times.
Currently, the framework assumes executions times are Rayleigh-distributed, however in literature these values are generally understood to follow an \gls{exGaussian} distribution.
Moreover, the utility of the framework could be significantly increased by considering extensions towards scenarios with multiple clients and a distributed solution.
